Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Typo

Previous experimental evaluations of the association graph model have used either maximal clique
enumeration algorithms \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08} (even when the
maximisation problem was being considered), or very simple maximum clique algorithms
\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}. Thus we re-evaluate the approach
using a modern maximum clique algorithm. Association graphs are dense, even if the input is sparse,
so we will using (the single-threaded, bit-parallel version of) the maximum clique solver by
McCreesh and Prosser \cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
\cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita
\textit{et al.}\
\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
bitset encoding due to San Segundo \textit{et al.}\
\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
``FC+Bound'' and ``MAC+Bound'' (simply referred to has FC and MAC) CP implementations of Ndiaye and
Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
used.

>>>>

Previous experimental evaluations of the association graph model have used either maximal clique
enumeration algorithms \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08} (even when the
maximisation problem was being considered), or very simple maximum clique algorithms
\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}. Thus we re-evaluate the approach
using a modern maximum clique algorithm. Association graphs are dense, even if the input is sparse,
so we will using (the single-threaded, bit-parallel version of) the maximum clique solver by
McCreesh and Prosser \cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
\cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita
\textit{et al.}\
\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
bitset encoding due to San Segundo \textit{et al.}\
\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
``FC+Bound'' and ``MAC+Bound'' (simply referred to as FC and MAC) CP implementations of Ndiaye and
Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
used.
